%Assignment
\noindent
	\textsc{\textbf{Miskolci Egyetem}}\\
Gépészmérnöki és Informatikai Kar\\
Alkalmazott Matematikai Intézeti Tanszék\hspace*{4cm}\hfil \textbf{Number:}

\vspace{0.5cm}
\begin{center}
\large\textsc{\textbf{Thesis Assignment}}
\end{center}
\vspace{0.5cm}

For the candidate: Péter Orosz (WO02D7), Computer Science major.

\bigskip
\noindent\textbf{Thesis topic:} Software Development

\bigskip
\noindent\textbf{Thesis title:} Cross-Platform Game Development in C++

\bigskip
\noindent\textbf{Task details:}

\medskip

\emph{The aim of the thesis is to develop a cross-platform game in C++ that demonstrates the application of modern software development principles and design patterns. The graphical rendering of the game should be implemented using the OpenGL library. However, the main focus of the project is not on the complexity of the gameplay itself, but on the reusability, extensibility, and maintainability of the code.}

\vfill

\noindent\textbf{Supervisor:} Dr. Péter Mileff (associate professor)

\bigskip
\noindent\textbf{Date of assignment: 2025-09-01}

\vspace{1.5cm}

\hfill\makebox[6cm]{\dotfill}

\hfill\makebox[6cm]{szakfelelős}

\clearpage

\vspace*{1cm}  
\begin{center}
\large\textsc{\textbf{Declaration of Originality}}
\end{center}
\vspace*{2cm}  

I, \textbf{Péter Orosz}; Neptun code: \texttt{WO02D7}, a final-year Computer Science student at University of Miskolc, Gépészmérnöki és Informatikai Kar, hereby declare under penalty of law and disciplinary responsibility that my thesis entitled \textit{Cross-Platform Game Development in C++} is my own independent work; all referenced literature has been used according to the rules of source management.

\medskip
I acknowledge that in the case of a thesis, plagiarism includes:
\begin{itemize}
\item presenting a literal quotation without quotation marks and reference;
\item presenting a content quotation without reference;
\item presenting another person's published ideas as my own.
\end{itemize}

I declare that I have understood the concept of plagiarism and acknowledge that in case of plagiarism, my thesis will be rejected.

\vspace*{3cm}

\noindent Miskolc, \makebox[2cm]{\dotfill} year \makebox[2cm]{\dotfill} month \makebox[2cm]{\dotfill} day

\vspace*{3cm}

\hfill\makebox[6cm]{\dotfill}

\hfill\makebox[6cm]{Student}



\clearpage

\newcommand{\ki}{Supervisor(s)}
\newsavebox{\alairas}
\begin{lrbox}{\alairas}
\begin{tabular}{c@{\hspace{2cm}}c}
\makebox[4cm]{\dotfill} & \makebox[5cm]{\dotfill} \\
date & \ki \\
\end{tabular}
\end{lrbox}
\newcommand{\dotline}{\makebox[5cm]{\dotfill}}
\newcommand{\shortdotline}{\makebox[3.5cm]{\dotfill}}

\noindent 1.
\begin{tabular}[t]{cl}
\multirow{2}{*}{Modification of thesis assignment}
&required (modification on a separate sheet) \\
&not required\\[1ex]
\end{tabular}

\begin{center}
\usebox{\alairas}
\end{center}

\smallskip

\noindent 2. I have checked the completion of the assignment:

\begin{center}
\begin{tabular}{c@{\hspace*{2cm}}c}
Supervisor (date, signature): & Consultant (date, signature):\\
\dotline & \dotline \\
\dotline & \dotline \\
\dotline & \dotline 
\end{tabular}
\end{center}

\smallskip

\noindent 3. The thesis can be submitted:

\begin{center}
\usebox{\alairas}
\end{center}

\noindent 4.
\begin{tabular}[t]{@{}l@{\hspace*{1mm}}l@{\hspace*{1mm}}l}
The thesis & \shortdotline & text pages\\
          & \shortdotline & program protocol (list, user manual)\\
          & \shortdotline & electronic data carrier (detailed)\\
          & \shortdotline \\
          & \shortdotline & other attachments (detailed)\\
          & \shortdotline 
\end{tabular}
\newline contains.

\begin{center}
\usebox{\alairas}
\end{center}

\noindent 5.
\begin{tabular}[t]{ll}
\multirow{2}{*}{The thesis for review} & can be submitted\\
& cannot be submitted\\
\end{tabular}

\smallskip

\noindent Name of reviewer: \makebox[8cm]{\dotfill}

\renewcommand{\ki}{szakfelelős}
\begin{center}
\begin{tabular}{c@{\hspace{2cm}}c}
\makebox[4cm]{\dotfill} & \makebox[5cm]{\dotfill} \\
date & \ki \\
\end{tabular}
\end{center}

\noindent 6.
\begin{tabular}[t]{lll}
Thesis grade \\
& supervisor's recommendation: & \makebox[2.5cm]{\dotfill} \\
& reviewer's recommendation: & \makebox[2.5cm]{\dotfill} \\
& final result of the thesis: & \makebox[2.5cm]{\dotfill}
\end{tabular}

\bigskip\bigskip

\noindent Miskolc, \makebox[4cm]{\dotfill} \hfill \makebox[8cm]{\dotfill} 

\hfill \makebox[8cm]{Chairman of the Final Examination Committee} 
